---
title: "Action Potential Propagation Pre-Processing"
author: Sierra Boyd
output:
  html_document:
    theme: cerulean
    toc: false
    code_folding: hide
editor_options: 
  chunk_output_type: console
---
#Load Packages
```{r}

library(tidyverse)
library(knitr)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggpubr)
library(data.table)
library(conflicted)
library(readxl)
library(openxlsx)
library(patchwork)

conflicts_prefer(purrr::transpose())
conflicts_prefer(dplyr::filter())

options(warn=-1)

```

```{r}
#Set wd to an an "export" folder
setwd("~")
```


#Import data files and arrange 
```{r}
#Indicate input directory
project.input.dir <-"~"

#Make list of data files 
branch_csv_files<- list.files(path=project.input.dir, pattern = "_branch_metrics\\.csv$", recursive = T, full.names = T) 
neuron_csv_files<- list.files(path=project.input.dir, pattern = "_neuron_metrics\\.csv$", recursive = T, full.names = T) 

#Make vector for what the names of the basenames of the data files
branch_data_frame_names<-gsub("_metrics.csv","",basename(branch_csv_files))
neuron_data_frame_names<-gsub("_metrics.csv","",basename(neuron_csv_files))

#Function to read in data files and make Group_IDs by separating assayTag
read_datafiles<-function(file){
  data<-read.csv(file)
  data$date<-gsub("-","",data$date)
  data$assayTag<-gsub(" ","_",data$assayTag)
  data<- data %>% separate(assayTag, c('DOP','Week','Type', 'PlateID'))
  data<-select(data,-c("DOP"))
  setnames(data,"div","DOP")
  data$Group_ID <- as.character(paste(data$"Group", data$"PlateID",data$"wellNo", sep = "_"))
  data$DOP_ID <- as.character(paste(data$"Group_ID", data$"DOP", sep = "_"))
  data<-as.data.frame(data)}

#Use the read_datafiles function made above to read in data files

branch_datalist<-lapply(branch_csv_files,read_datafiles)
neuron_datalist<-lapply(neuron_csv_files,read_datafiles)

#Assign the names from the vector data_frame_names to the data frames just read in
for (i in seq_along(branch_datalist)){
  assign(branch_data_frame_names[i],branch_datalist[[i]])
}

for (j in seq_along(neuron_datalist)){
  assign(neuron_data_frame_names[j],neuron_datalist[[j]])
}


#Retrive the actual data frames
branch_data_frames<-mget(branch_data_frame_names)
neuron_data_frames<-mget(neuron_data_frame_names)

#combine data frames into new df
branch_full<-rbindlist(branch_data_frames,use.names=TRUE,fill=TRUE) 
neuron_full<-rbindlist(neuron_data_frames,use.names=TRUE,fill=TRUE) 
```

#Join all data files forming AllMetrics df
```{r}
#Select columns needed
neuron_full<-select(neuron_full, c("DOP_ID","date","neuronConductionVel","totalAxonLen","longestBranchLen","longestDistFromInitSite","longestLat","amplitudeInitSite","totNoSpikes","neuronFiringRate"))

#Make vector with endpoint names
neuron_metric<-c("neuronConductionVel","totalAxonLen","longestBranchLen","longestDistFromInitSite","longestLat","amplitudeInitSite","totNoSpikes","neuronFiringRate")

#Summarize by DOP_ID for all endpoints
neuron_full<-neuron_full %>%
  mutate(across(all_of(neuron_metric),as.numeric))%>%
  group_by(DOP_ID,date) %>%
  summarize(across(all_of(neuron_metric), list(mean=mean),na.rm=TRUE))

#vector of columns to add _Neuron to colname 
columns_to_add_neuron<-c("neuronConductionVel_mean","totalAxonLen_mean","longestBranchLen_mean","longestDistFromInitSite_mean","longestLat_mean","amplitudeInitSite_mean","totNoSpikes_mean","neuronFiringRate_mean")

#function to add _Neuron to colname
add_neuron<-function(df,columns){
  for(col in columns){
    neuron_col_name<-paste0(col, "_neuron")
    names(df)[names(df)==col]<-neuron_col_name
  }
  return(df)
}

#apply function
neuron_full<-add_neuron(neuron_full,columns_to_add_neuron)

#Do the same for branch data
#Select columns needed
branch_full<-select(branch_full, c("DOP_ID","date","branchLen","branchConductionVel","conductionVelFit","latFromInitSite","distFromInitSite","totNoSpikes","neuronFiringRate","spikesNoPerConfig_mean","completeness","fisherProjectionDistance","silhouetteScore"))

#Make vector with endpoint names
branch_metrics<-c("branchLen","branchConductionVel","conductionVelFit","latFromInitSite","distFromInitSite","totNoSpikes","neuronFiringRate","spikesNoPerConfig_mean","completeness","fisherProjectionDistance","silhouetteScore")

#Summarize by DOP_ID for all endpoints
branch_full<-branch_full %>%
  mutate(across(all_of(branch_metrics),as.numeric))%>%
  group_by(DOP_ID,date) %>%
  summarize(across(all_of(branch_metrics), list(mean=mean),na.rm=TRUE))

#vector of columns to add _Neuron to colname 
columns_to_add_branch<-c("branchLen_mean","branchConductionVel_mean","conductionVelFit_mean","latFromInitSite_mean","distFromInitSite_mean","totNoSpikes_mean","neuronFiringRate_mean","spikesNoPerConfig_mean_mean","completeness_mean","fisherProjectionDistance_mean","silhouetteScore_mean")

#function to add _Neuron to colname
add_branch<-function(df,columns){
  for(col in columns){
    branch_col_name<-paste0(col, "_branch")
    names(df)[names(df)==col]<-branch_col_name
  }
  return(df)
}

#apply function
branch_full<-add_branch(branch_full,columns_to_add_branch)

#Merge dfs making AllMetrics df
AllMetrics<-dplyr::full_join(branch_full,neuron_full,by=c("DOP_ID","date"))
AllMetrics$newcol<-AllMetrics$DOP_ID
AllMetrics<- AllMetrics %>% separate(newcol, c('Group','PlateID','wellNo', 'DOP'))
AllMetrics$Group_ID <- as.character(paste(AllMetrics$"Group", AllMetrics$"PlateID",AllMetrics$"wellNo", sep = "_"))
AllMetrics<-select(AllMetrics,-c("Group","PlateID","wellNo"))

```

#Import Meta files and merge meta with data df
```{r}
#Make list of meta files
Meta_file<-list.files(path=project.input.dir,pattern="_Meta\\.csv$", recursive = T, full.names = T)

#Read in meta files and make Group_IDs, and join with fulldata df, make Endpoint columns numeric
for (j in Meta_file){
  meta<-read.csv(j)
  meta$wellNo<-as.character(meta$wellNo)
  meta$PlateID<-as.character(meta$PlateID)
  meta$Group_ID <- as.character(paste(meta$"Group", meta$"PlateID",meta$"wellNo", sep = "_"))
  meta<-select(meta,-c("PlateID","wellNo","Group"))
  AllMetrics <- dplyr::full_join(meta,AllMetrics, by = "Group_ID")
  AllMetrics[,8:27]<-lapply(AllMetrics[,8:27],as.numeric)
  AllMetrics<-subset(AllMetrics %>% filter(!grepl("Detached",Notes)))
  AllMetrics<-AllMetrics %>% distinct(DOP,Chemical,Dosage,Group_ID,DOP_ID, .keep_all=TRUE) #remove any duplicates
order<-c(6,8,13,15,20,22,27,29)
AllMetrics$DOP<-factor(AllMetrics$DOP,levels=order)
Doseorder<-c("Control",0.03,0.1,0.3,1,3,10,30,100)
AllMetrics$Dosage<-factor(AllMetrics$Dosage,levels=Doseorder)
AllMetrics<-AllMetrics[complete.cases(AllMetrics$DOP),]
  }
```


#Make a melted table to export for tcplfit2 or AUC analysis
```{r}
#Melt table to long format
Axon_Tracking_Melt <- melt(AllMetrics, id.vars = c("DOP","date","Chemical","Dosage","Group_ID"),
                          measure.vars =c(
"branchLen_mean_branch",                "branchConductionVel_mean_branch",      "conductionVelFit_mean_branch",        
"latFromInitSite_mean_branch",          "distFromInitSite_mean_branch",         "totNoSpikes_mean_branch",             
"neuronFiringRate_mean_branch",         "spikesNoPerConfig_mean_mean_branch",   "completeness_mean_branch",            
"fisherProjectionDistance_mean_branch", "silhouetteScore_mean_branch",          "neuronConductionVel_mean_neuron",     
"totalAxonLen_mean_neuron",             "longestBranchLen_mean_neuron",         "longestDistFromInitSite_mean_neuron", 
"longestLat_mean_neuron",               "amplitudeInitSite_mean_neuron",        "totNoSpikes_mean_neuron",             
"neuronFiringRate_mean_neuron"))

#Update variable names
setnames(Axon_Tracking_Melt, "variable","Endpoint")

#Save as a CSV
write.csv(Axon_Tracking_Melt,file = "~",row.names=F)

```

#Plot controls overtime by plate type
```{r}
#Set Plate Types. If plate serial number starts with T than it is a 24-well plate, M is for 6-well plates
Axon_Tracking_Melt<-Axon_Tracking_Melt%>%
  mutate(Plate_Type=ifelse(grepl("T",Group_ID),"Twenty Four","Six"))

#Isolate Controls
Axon_Tracking_Melt_Controls <-Axon_Tracking_Melt%>%  filter((Dosage== "Control"))

#Check for NAs and remove
Axon_Tracking_Melt_Controls<-subset(Axon_Tracking_Melt_Controls,!is.na(value))

#Set variables as factors
Axon_Tracking_Melt_Controls$DOP<-as.factor(Axon_Tracking_Melt_Controls$DOP)
Axon_Tracking_Melt_Controls$value<-as.numeric(Axon_Tracking_Melt_Controls$value)

#Check for duplicates and remove
Axon_Tracking_Melt_Controls<-Axon_Tracking_Melt_Controls%>%distinct(Group_ID,DOP,Chemical, Dosage, Plate_Type, value, Endpoint,.keep_all=TRUE)

#Update Endpoint Names
Axon_Tracking_Melt_Controls$Endpoint<-gsub("branchLen_mean_branch","Branch Length (µm)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("branchConductionVel_mean_branch","Conduction Velocity (m/s)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("conductionVelFit_mean_branch","Conduction Velocity Coefficient of Variation-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("latFromInitSite_mean_branch","Latency from Initation Site Velocity (ms)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("distFromInitSite_mean_branch","Distance from Initation Site (µm)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("neuronFiringRate_mean_branch","Firing Rate (Hz)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("spikesNoPerConfig_mean_mean_branch","Number of Spikes per Configuration-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("completeness_mean_branch","Completeness-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("fisherProjectionDistance_mean_branch","Fisher Projection Distance-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("neuronConductionVel_mean_neuron","Conduction Velocity (m/s)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("totalAxonLen_mean_neuron","Total Axon Length (µm)-Branch",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("longestBranchLen_mean_neuron","Longest Branch Length (µm)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("longestDistFromInitSite_mean_neuron","Longest Distance from Initation Site (µm)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("longestLat_mean_neuron","Longest Latency (ms)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("amplitudeInitSite_mean_neuron","Amplitude at Initiaiton Site (Hz)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("totNoSpikes_mean_neuron","Number of Spikes per Neuron-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("neuronFiringRate_mean_neuron","Firing Rate (Hz)-Neuron",Axon_Tracking_Melt_Controls$Endpoint)
Axon_Tracking_Melt_Controls$Endpoint<-gsub("silhouetteScore_mean_branch","Silhouette Score",Axon_Tracking_Melt_Controls$Endpoint)

#Graph each endpoint over time for each plate type
AxonTracking_By_PlateType<-ggplot(Axon_Tracking_Melt_Controls,aes(x=as.factor(DOP),y=value,fill=Plate_Type,color=Plate_Type,shape=Plate_Type))+
   geom_boxplot()+
  geom_point(position=position_dodge(width=0.75))+
  theme_minimal()+
  labs(
  y=paste(""),
  x="Days on Plate")+
  scale_fill_manual(values=c("grey90","grey20"))+
  scale_color_manual(values=c("grey40","grey10"))+
  scale_shape_manual(values=c(15,19))+
  facet_wrap(~Endpoint,scales="free",ncol=4)+
  theme(legend.position = "NULL")+ 
  theme(strip.text.x = element_text(size = 7.9))

AxonTracking_By_PlateType

#Save
ggsave("AxonTracking_By_PlateType.png",plot=AxonTracking_By_PlateType,bg="white",width=10.4,height=7)

```

#Plot controls over time
```{r}

#Edit Endpoint Names
Axon_Tracking_Melt$Endpoint<-gsub("branchLen_mean_branch","Branch Length (µm)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("branchConductionVel_mean_branch","Conduction Velocity (m/s)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("conductionVelFit_mean_branch","Conduction Velocity Coefficient of Variation-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("latFromInitSite_mean_branch","Latency from Initation Site Velocity (ms)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("distFromInitSite_mean_branch","Distance from Initation Site (µm)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("neuronFiringRate_mean_branch","Firing Rate (Hz)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("spikesNoPerConfig_mean_mean_branch","Number of Spikes per Configuration-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("completeness_mean_branch","Completeness-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("fisherProjectionDistance_mean_branch","Fisher Projection Distance-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("neuronConductionVel_mean_neuron","Conduction Velocity (m/s)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("totalAxonLen_mean_neuron","Total Axon Length (µm)-Branch",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("longestBranchLen_mean_neuron","Longest Branch Length (µm)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("longestDistFromInitSite_mean_neuron","Longest Distance from Initation Site (µm)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("longestLat_mean_neuron","Longest Latency (ms)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("amplitudeInitSite_mean_neuron","Amplitude at Initiaiton Site (Hz)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("totNoSpikes_mean_neuron","Number of Spikes per Neuron-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("neuronFiringRate_mean_neuron","Firing Rate (Hz)-Neuron",Axon_Tracking_Melt$Endpoint)
Axon_Tracking_Melt$Endpoint<-gsub("longestDistFromInitSite_mean_summary","Longest Distance from Initation Site Length (µm)-Well",Axon_Tracking_Melt$Endpoint)

Axon_Tracking_Melt_Controls$Endpoint<-gsub("silhouetteScore_mean_branch","Silhouette Score",Axon_Tracking_Melt_Controls$Endpoint)


#Set DOPs as a factor with levels for graphing 
order<-c(6,8,13,15,20,22,27,29)
Axon_Tracking_Melt$DOP<-factor(Axon_Tracking_Melt$DOP,levels=order)

#Subset controls
fulldata_control <-Axon_Tracking_Melt%>%  filter((Dosage== "Control"))

#check for duplicated rows and remove
fulldata_control<-fulldata_control%>%distinct(Group_ID,DOP,Endpoint,.keep_all=TRUE)

#Make vector of the unique endpoints
Endpoint<-unique(fulldata_control$Endpoint)

#Make empty list for plots 
AxonTracking_Control_BoxPlots_plotlist<-list()

#ForLoop to plot all Endpoints
for (k in Endpoint){
   df_subset<-fulldata_control[fulldata_control$Endpoint==k,]
  
  AxonTracking_Control_BoxPlots<-ggplot(df_subset,aes(x=factor(DOP),y=value,color=DOP))+
  theme_minimal()+
  labs(y=k,x="Days on Plate")+
  scale_color_manual(values=c("black","black","black","black","black","black","black","black","black","black","black","black"))+
  geom_boxplot(alpha=0.6,position = position_dodge(width=0.7))+
  geom_point(position = position_dodge(width=0.7))+
  theme(axis.title.y = element_text(size = 7.8))+
 theme(legend.position="none")
    
   print(AxonTracking_Control_BoxPlots)
  
   AxonTracking_Control_BoxPlots_plotlist[[k]]<-AxonTracking_Control_BoxPlots
}

#Put all plots in one figure and save
AxonTracking_Control_BoxPlots<-ggarrange(plotlist=AxonTracking_Control_BoxPlots_plotlist)
AxonTracking_Control_BoxPlots<-annotate_figure(AxonTracking_Control_BoxPlots, top = text_grob("Activity Tracking Ontogeny for Controls",size=14))
AxonTracking_Control_BoxPlots

ggsave("AxonTracking_Control_BoxPlots.png",plot=AxonTracking_Control_BoxPlots,bg="white",width=14,height=14)

```

#Normalize data to control
```{r}
Controls_long<-fulldata_control

Axon_Tracking_Melt$Endpoint<-as.character(Axon_Tracking_Melt$Endpoint)

#Find mean of control data by DOP and Endpoint
Controls_long<-Controls_long%>% group_by(DOP,Endpoint,Plate_Type) %>% 
  summarize(control=mean(value))%>%
  ungroup()

#Merge back to df
fulldata <- full_join(Axon_Tracking_Melt,Controls_long, by = c("DOP","Endpoint","Plate_Type"))

fulldata<-fulldata%>%group_by(DOP,Chemical,Dosage,Group_ID,Endpoint,Plate_Type) %>% 
  summarize(Norm=((value/control)*100)) %>%
  ungroup()

#Remove duplicated rows
fulldata<-fulldata%>%distinct(Group_ID,DOP,Endpoint,Chemical,Plate_Type,.keep_all=TRUE)

fulldata<-as.data.frame(fulldata)

is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))

fulldata[is.nan(fulldata)] <- NA


```

#Calculate se
##For graphing to only show down direction error bars
```{r}
#Make se function
se <- function(x) {
  sd(x) / sqrt(length(x))
}

#calculate se
se_results<-fulldata%>% group_by(DOP,Endpoint,Dosage,Chemical) %>% 
  summarise(se = se(Norm))%>%
  ungroup()

#Full join back to data
fulldata<-full_join(fulldata,se_results, by=c("Chemical","DOP","Dosage","Endpoint"))

#Remove duplicated rows
fulldata<-fulldata%>%distinct(Group_ID,DOP,Endpoint,Chemical,Dosage,Plate_Type,.keep_all=TRUE)

```

#Find mean of the Norm data
```{r}
#calculate mean
fulldata<-fulldata%>% group_by(DOP,Endpoint,Dosage,Chemical,se) %>% 
  summarise(Mean = mean(Norm))%>%
  ungroup()
```

#Filter out pre-treatment days and washout days
```{r}
#filter out DOP 2 which is a pre-treatment date
fulldata <- fulldata %>% filter(DOP != 2)

#edit variable names
setnames(fulldata,"Chemical","trt")
setnames(fulldata,"Dosage","dose")
setnames(fulldata,"DOP","DIV")

#Fix endpoint names
fulldata$Endpoint<-gsub("totNoSpikes_mean_branch","Number of Spikes per Neuron-Branch",fulldata$Endpoint)
fulldata$Endpoint<-gsub("silhouetteScore_mean_branch","Silhouette Score-Branch",fulldata$Endpoint)
```

#Plot Line graphs
```{r}
Endpoint<-unique(fulldata$Endpoint)
Chemical<-unique(fulldata$trt)

fulldata<-as.data.table(fulldata)

plotlist<-list()
res1<-list()

for (p in Chemical){
  df_chemical<-fulldata%>%filter(trt==p)
  
  for (o in Endpoint){
    df_endpoint<-df_chemical %>% filter(Endpoint==o)
    
    p_plot<-ggplot(df_endpoint,aes(x=factor(DIV),y=Mean,group=dose,color=factor(dose)))+
                     geom_point(size=2.5,aes(shape=factor(dose),color=factor(dose)))+
                     geom_line(size=1.25,alpha=0.6,aes(color=factor(dose)))+
                    geom_errorbar(aes(ymin=Mean-se,ymax=Mean),width=0.3,alpha=0.8)+
                    scale_color_manual(values=c("gray20","darkgreen","springgreen2","turquoise3","dodgerblue3","navy"))+
                    scale_shape_manual(values=c(15,16,17,18,7,10))+ 
                    geom_hline(yintercept=100,linetype="dashed",color="black")+
                     labs(title=paste(p),
                          y=paste(o,"(% of Control)", sep=" "),
                          x="Days on Plate",
                          color="Concentration (uM)",
                          shape="Concentration (uM)")+
                     theme_minimal()
                   
                   print(p_plot)
                  plotlist[[o]]<-p_plot
  }
  res1<-list(res1,plotlist)
}

Total_plots<-list(res1)
pdf("AxonTracking_LineGraphs.pdf",width=7,height=5)
for (plot in Total_plots){
  print(plot)
}

dev.off()

```


#Plot only number of spikes per neuron
```{r}

FR_Neuron <- fulldata %>% filter(Endpoint == "Firing Rate (Hz)-Neuron")

FR_Neuron_plotlist<-list()
res2<-list()

 for (q in Chemical){
    Chem_df<-FR_Neuron %>% filter(trt==q)
    
    p_plot2<-ggplot(Chem_df,aes(x=factor(DIV),y=Mean,group=dose,color=factor(dose)))+
                     geom_point(size=2.5,aes(shape=factor(dose),color=factor(dose)))+
                     geom_line(size=1.25,alpha=0.6,aes(color=factor(dose)))+
                    geom_errorbar(aes(ymin=Mean-se,ymax=Mean),width=0.3,alpha=0.8)+
                    scale_color_manual(values=c("gray20","darkgreen","springgreen2","turquoise3","dodgerblue3","navy"))+
                    scale_shape_manual(values=c(15,16,17,18,7,10))+ 
                    geom_hline(yintercept=100,linetype="dashed",color="black")+
                     labs(title=paste(q),
                          y=(bquote('Firing Rate - Neuron (Hz)\n(% of Control)')),
                          x="Days on Plate",
                          color="Concentration (uM)",
                          shape="Concentration (uM)")+
                     theme_minimal()+
                    ylim(0,250)
                  
                   print(p_plot2)
                  FR_Neuron_plotlist[[q]]<-p_plot2
  }
  res2<-list(res2,FR_Neuron_plotlist)
```

```{r}
plts_for_fig<-patchwork::wrap_plots(FR_Neuron_plotlist,ncol=2)
plts_for_fig

ggsave("Axon_LineGraphs_forFig.png",plot=plts_for_fig,bg="white",width=13,height=4.6)
```


